---
title: "Basic Inferential Data Analysis: Tooth Growth"
author: "Christian Ibanez"
date: "August 28, 2018"
output: html_document
---
Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

Load the ToothGrowth data and perform some basic exploratory data analyses
Provide a basic summary of the data.
Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
State your conclusions and the assumptions needed for your conclusions.

Load dataset
```{r}
library(datasets)
data("ToothGrowth")
```

Number of rows of dataset
```{r}
nrow(ToothGrowth)
```

View
```{r}
View(ToothGrowth)
```

Convert variable dose from numeric to factor
```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

Look at the dataset variables after conversion
```{r}
str(ToothGrowth)
```

Summary statistics
```{r}
summary(ToothGrowth)
```

Split of cases between different dose levels and delivery methods
```{r}
table( ToothGrowth$supp,ToothGrowth$dose)
```

Use confidence interval and hypothesis tests to compare tooth growth by supp and dose
Check for group difference due to different supplement type

```{r}
#assuming unequal variance between the two groups
t.test(len ~ supp, data = ToothGrowth)

#assuming equal variance between the two groups
t.test(len ~ supp, data = ToothGrowth, var.equal = TRUE)
#p is low == no statistical significant difference
```

Create 3 sub-groups asa per dose level pair
```{r}
ToothGrowth.dose_0.5_1 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
ToothGrowth.dose_1_2 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))
ToothGrowth.dose_0.5_2 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))
```

ASSUMING UNEQUAL VARIANCE

```{r}
#Check for group difference,dose levels (0.5, 1)
#assuming unequal variances between 2 groups
t.test(len ~ dose, data = ToothGrowth.dose_0.5_1)
# Check for group differences,dose levels (0.5, 2)
# assuming unequal variances between the two groups
t.test(len ~ dose, data = ToothGrowth.dose_0.5_2)
# Check for group differences,dose levels (1, 2)
# assuming unequal variances between the two groups
t.test(len ~ dose, data = ToothGrowth.dose_1_2)
```


ASSUMING EQUAL VARIANCE
```{r}
#Check for group difference, dose levels (0.5, 1)
#assuming equal variances between 2 groups
t.test(len ~ dose, data = ToothGrowth.dose_0.5_1, var.equal = TRUE)
# Check for group differences, dose levels (0.5, 2)
# assuming equal variances between the two groups
t.test(len ~ dose, data = ToothGrowth.dose_0.5_2, var.equal = TRUE)
# Check for group differences, dose levels (1, 2)
# assuming equal variances between the two groups
t.test(len ~ dose, data = ToothGrowth.dose_1_2, var.equal = TRUE)
```


Conclusion:
The type of supplement delivery doesn't have a significant effect on tooth growth but the amount of dosage of Vitamin C has a significant effect on tooth growthh

Assumption:
Tooth growth data follows a normal distribution



