My First R Markdown File (from scratch)
======================================

This is my first R markdown file.

```{r setoptions, echo=FALSE}
#opts_chunk$set(echo = FALSE, results = "hide")

```


Here, we're going to load some data.

```{r}
library(datasets)
data("airquality")
summary(airquality)
```

#### Let's first make a pairs plot of the data.

```{r echo=TRUE}
pairs(airquality)
```

#### Here's a regression model of ozone on wind, solar radiation, and temperature.

Variables for the Regression Model  

* Wind

* Solar Radiation

* Temperature

```{r}
library(stats)
fit <- lm(Ozone ~ Wind + Solar.R + Temp, data = airquality)
summary(fit)
```

#### Here's another regression model of ozone but using the day and month.

Variables for the Regression Model  

* Month

* Day

```{r}
fit2 <- lm(Ozone ~ Month + Day, data = airquality)
summary(fit2)
```
#### Is Temperature alone a good predictor for Ozone?

Variables for the Regression Model  

* Temperature


```{r}
fit3 <- lm(Ozone ~ Temp, data = airquality)
summary(fit3)
```

### Inputing actual variables in a text

```{r, echo= FALSE}
time <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```
The current time is `r time`. My favorite random number is `r rand``

### Incorporating Graphics
```{r, echo= TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```

Here is a scatterplot of the data

```{r scatterplot, fig.height=4}
plot(x,y, main = "My Simulated Data")
```

### Making Tables with xtable

## Introduction
```{r fitmodel}
library(datasets)
data("airquality")
fit <- lm(Ozone ~ Wind + Temp + Solar.R, data = airquality)
```
Here is a table of regression coefficients.

```{r showtable, results='asis'}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type = "html")
```





